### 2017-01-27 manuscript.rmd
typo

		# Add a colmn with the gene tree hash 
		D %<>% mutate( gene_tree = digest( nhx ) )

@@

		# For each row, bet the most recent common ancestor of the pairwise tip combination
		D$mrca = 
			apply(
				D, 
				1, 
				function( y ) ape::getMRCA( 
					nhx@phylo, 
					c( as.integer( y['tip_a'] ), as.integer( y['tip_b'] ) )
				)
			) %>%
			as.integer()

		# Merge data on this mrca to the node
		D %<>% left_join(
			nhx@data %>%
				select( D, node, node_age, pic ),
			by = c( "mrca" = "node")

>>>>

		# Add a column with the gene tree hash 
		D %<>% mutate( gene_tree = digest( nhx ) )

@@

		# For each row, get the most recent common ancestor of the pairwise tip combination
		D$mrca = 
			apply(
				D, 
				1, 
				function( y ) ape::getMRCA( 
					nhx@phylo, 
					c( as.integer( y['tip_a'] ), as.integer( y['tip_b'] ) )
				)
			) %>%
			as.integer()

		# Merge data of this mrca to the node
		D %<>% left_join(
			nhx@data %>%
				select( D, node, node_age, pic ),
			by = c( "mrca" = "node")
